Datasheet for League of Legend Player Performance KDA analysis Dataset

### 2024-11-27 other/datasheet/datasheet_template.qmd
update paper and datasheet

---
title: "Datasheet for 'A dataset'"
author: 
  - Colin Sihan Yang
thanks: "Code and data are available at: [https://github.com/hoodiexxx/lol_win_rate_prediction](https://github.com/hoodiexxx/lol_win_rate_prediction)."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: pdf
number-sections: true
bibliography: ../../paper/references.bib
---

>>>>

---
title: "Datasheet for League of Legend Player Performance KDA analysis Dataset"
author: 
  - Colin Sihan Yang
thanks: "Code and data are available at: [https://github.com/hoodiexxx/lol_win_rate_prediction](https://github.com/hoodiexxx/lol_win_rate_prediction)."
date: today
format: pdf
number-sections: true
bibliography: ../../paper/references.bib
---
